Final Project Part 3 Report

### 2024-12-07 final_paper/final_report.Rmd
final

According to the topic of house prices and its influencers, we download the dataset with relevant predictors from Statistics Canada (Statistics Canada, 2024). The New Housing Price Index (NHPI) was defined as the response variable, with 13 predictors identified, including absorption (detached-absorption, semi-absorption, detached-unabsorbed, semi-unabsorbed), GDP, CPI, and construction (starting-detached-construction, starting-semi-construction, under construction detached, under construction-semi, completed-construction-detached, completed-construction-semi).

@@

Government of Canada, Statistics Canada, S. C. (2024, November 19). Consumer price index, monthly, not seasonally adjusted. Consumer Price Index, monthly, not seasonally adjusted. https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=1810000401

>>>>

According to the topic of house prices and its influencers, we download the dataset with relevant predictors from Statistics Canada (Statistics Canada, 2024). The New Housing Price Index (NHPI) (Government of Canada, Statistics Canada, 2017) was defined as the response variable, with 13 predictors identified, including absorption (detached-absorption, semi-absorption, detached-unabsorbed, semi-unabsorbed), GDP, CPI, and construction (starting-detached-construction, starting-semi-construction, under construction detached, under construction-semi, completed-construction-detached, completed-construction-semi).

@@

Government of Canada, Statistics Canada, S. C. (2024a, October 16). Canada mortgage and Housing Corporation, housing starts, under construction and completions, all areas, quarterly. Canada Mortgage and Housing Corporation, housing starts, under construction and completions, all areas, quarterly. https://doi.org/10.25318/3410013501-eng

Government of Canada, Statistics Canada, S. C. (2024b, November 19). Consumer price index, monthly, not seasonally adjusted. Consumer Price Index, monthly, not seasonally adjusted. 
https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=1810000401

Government of Canada, Statistics Canada, S. C. (2024c, November 19). Consumer price index, monthly, not seasonally adjusted. Consumer Price Index, monthly, not seasonally adjusted. 
https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=1810000401

Government of Canada, Statistics Canada, S. C. (2024d, November 20). Canada mortgage and Housing Corporation, absorptions and unabsorbed inventory, newly completed dwellings, by type of dwelling unit in census metropolitan areas. Canada Mortgage and Housing Corporation, absorptions and unabsorbed inventory, newly completed dwellings, by type of dwelling unit in census metropolitan areas. https://doi.org/10.25318/3410014901-eng

Government of Canada, Statistics Canada, S. C. (2024e, November 29). Financial Market Statistics, last Wednesday unless otherwise stated, Bank of Canada. Financial market statistics, last Wednesday unless otherwise stated, Bank of Canada. https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=1010012201

Government of Canada, Statistics Canada, S. C. (2024f, November 29). Gross domestic product (GDP) at basic prices, by industry, monthly. https://doi.org/10.25318/3610043401-eng
